---
title: "R Example"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

```{r}
library(rfigshare)
library(tidyverse)
```


## Download data

I'm using Rebecca Senior's beautifully documented data reposit [***Data for: Tropical forests are thermally buffered despite intensive selective logging***](https://figshare.com/articles/Data_for_Tropical_forests_are_thermally_buffered_despite_intensive_selective_logging/5414629/1)


```{r, eval=FALSE}
fs_download(5414629)
```

This call sends you to a figshare page which prompts you for authentication. Once authenticated, the function runs.


Calling the function returns the download URLs of the objects associated with the article. Also, **giving just the article number downloads the latest version** of the materials. Use`show_versions = T` to see what versions are available and specify a  version through argument `version`.


```{r, eval=FALSE}
fs_download(5414629)
```



### BUG! 
```{r}
fs_download(5414629, version = 3)
fs_download(5414629, show_versions = T)
```
 
Let's download the actual data using argument
```{r}
urls <- fs_download(5414629)
```

```{r}
data <- read_csv(urls[1,1])
data
```




```{r}
metadata <- read_csv(urls[2,1])
metadata
```

### Plot map

```{r, message=F}
library(leaflet)
library(sp)
```


```{r}
names(providers) %>% head()
```
### Convert data to SpatialPolygonDataFrame
```{r}
shp <- data
coordinates(shp) <- ~ longitude + latitude
```

## Map
```{r}

leaflet(shp) %>%
   addProviderTiles(providers$Esri.WorldImager) %>% 
    addMarkers(popup = ~as.character(plotID), label = ~as.character(plotID))
```




```{r}
greenLeafIcon <- makeIcon(
  iconUrl = "http://leafletjs.com/examples/custom-icons/leaf-green.png",
  iconWidth = 15, iconHeight = 40,
  iconAnchorX = 22, iconAnchorY = 94,
  shadowUrl = "http://leafletjs.com/examples/custom-icons/leaf-shadow.png",
  shadowWidth = 3, shadowHeight = 14,
  shadowAnchorX = 0, shadowAnchorY = 4
)

leaflet(shp) %>%
   addProviderTiles(providers$Esri.WorldImager) %>% 
    addMarkers(popup = ~as.character(plotID), label = ~as.character(plotID), icon = greenLeafIcon)
```
